# Data
```{r}
library(ggplot2)
library(dplyr)
library(tidyverse)
library(heatmaply)


salary=read.csv('Citywide_Payroll_Data__Fiscal_Year_ (1).csv')
#delete meaningless data
salary=salary[, -which(colnames(salary) %in% c("Payroll.Number","Last.Name","First.Name","Mid.Init"))]
head(salary)
```
## Description
Data sources: The Citywide Payroll dataset is from NYC OpenData website. https://data.cityofnewyork.us/City-Government/Citywide-Payroll-Data-Fiscal-Year-/k397-673e/data

Data collection: Data Provided by Office of Payroll Administration (OPA). Data is input into the City's Personnel Management System (“PMS”) by the respective user Agencies. It includes the agency information, salary and overtimepay for all municipal employees in New York.

Data description:
Data is collected because of public interest in how the City’s budget is being spent on salary and overtime pay for all municipal employees.

1.format
We summarize it by a csv file.
```{r}
des=read.csv('data_description.csv')
print(des)
```
2.frequency of updates:   It is updated annually.

3.dimension:   5662713*13
```{r}
dim(salary)
```

4.data range: 
For numerical data:
    Fiscal.Year  2014 to 2023
    Agency.Start.Date        
    Base.Salary 0.01 to 414707
    Regular.Hours -1260.00 to 6666.00
    Regular.Gross.Paid  -117006.33 to  672308.86       
    OT.Hours  -127.00 to 3692.90
    Total.OT.Paid  -14811.51 to 255999.85
```{r}
max_values <- apply(salary[c("Fiscal.Year","Base.Salary","Regular.Hours","Regular.Gross.Paid","OT.Hours","Total.OT.Paid")], 2, max)
min_values <- apply(salary[c("Fiscal.Year","Base.Salary","Regular.Hours","Regular.Gross.Paid","OT.Hours","Total.OT.Paid")], 2, min)
print('upper bound')
print(max_values)
print('lower bound')
print(min_values)
```
For categorical data:
```{r}
#table(salary[c("Agency.Name")])
table(salary[c("Work.Location.Borough")])
#table(salary[c("Title.Description")])
table(salary[c("Leave.Status.as.of.June.30")])

```

5.Issues / problems with the data
i.There exists negative Regular Hours and OT hours.
ii.Agency start date exists 12/31/9999.

6.how to impute data
We download Citywide Payroll dataset on NYC OpenData website in 'csv' format and impute it by read.csv function directly.
https://data.cityofnewyork.us/City-Government/Citywide-Payroll-Data-Fiscal-Year-/k397-673e/data

## Research Plan
Core Topic:
The Impact of Agency Characteristics on Employee Compensation and Work Patterns.
We will introduce our research questions from the introduction into 3 parts:
1.




2. Overtime Analysis(OT column)

i. Identify patterns and causes of overtime across agencies and job titles by detecting the relationship between agency,Agency start time,year,Work location,job Title and overtime respectively. Once the main causes are found, we search for the prevalent characters in these causes. (From our guess, it should include job titles or agencies)

ii. Determine if overtime is the norm. Analyze the ratio of regular hours to overtime hours across different agencies.


3. Multi-factor mixed analysis 
Analyzing the relationship between employment duration, salary, and rank within agencies. Here we plan to choose mosaic and slope graph as analysis tool.


## Missing value analysis
```{r}
# Counting missing values per column
missing_values <- sapply(salary, function(x) sum(is.na(x)))

# Creating the bar chart
ggplot(data = data.frame(Column = names(missing_values), MissingValues = missing_values), 
       aes(x = Column, y = MissingValues)) +
    geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(x = "Column Name", y = "Number of Missing Values", title = "Missing Values per Column")

```
